%!TEX root = Bericht.tex
\begin{thebibliography}{99}
%\addcontentsline{toc}{chapter}{Literaturverzeichnis}
\addcontentsline{toc}{chapter}{Bibliography}



%\bibitem {comfilt} {\sc R.~Mahony, T.~Hamel, J.-M.~Pflimlin}:
%{\it Complementary filter design on the special orthogonal group SO(3)}. In 45th Conference
%on Decision and Control CDC'05, Seville, Spain, 2005.
\bibitem{schaffnervu}{\sc A.~Schaffner, N.~Vuilliomenet}:
{\it Blimp Actuation Chain Modeling and Optimization}. BSc thesis, ETH Zurich, 2012.
\bibitem {weichart} {\sc J.~Weichart}:
{\it Agile Blimp Modeling and Simulation Environment}. BSc thesis, ETH Zurich, 2012.
\bibitem {kammermann} {\sc T.~Kammermann}:
{\it Evaluation and implementation of a control device for a ballbot}. BSc thesis, ETH Zurich, 2010.
\bibitem {meiermueri} {\sc D.~Meier, L.~M{\"u}ri}:
{\it Agile Blimp Controller Design}. BSc thesis, ETH Zurich, 2012.
\bibitem{burri}{\sc M.~Burri}:
{\it Communication Software for a Blimp}. BSc thesis, ETH Zurich, 2012.
\bibitem{blanchette}{\sc J.~Blanchette, M~Summerfield}:
{\it C++ GUI Programming with Qt 4}. Prentice Hall, Upper Saddle River, N.J., 2010.
\bibitem {snider} {\sc J. M.~Snider}:
{\it Automatic Steering Methods for Autonomous Automobile Path Tracking}. Research Report CMU-RI-TR-09-08, Robotics Institute Carnegie Mellon University Pittsburgh, Pennsylvania, 2009.
\bibitem{dahmen}{\sc W.~Dahmen, A.~Reusken}:
{\it Numerik f{\"u}r Ingenieure und Naturwissenschaftler}. Springer Verlag, Berlin, 2006.
\bibitem{stammbach}{\sc U.~Stammbach}:
{\it Analysis I/II, Teil A}. ETH Zurich, 2005.
\bibitem{haron}{\sc H. Haron, [et al.]}:
{\it Parameterization Method on B-Spline Curve}. Mathematical Problems in Engineering, vol. 2012.
\bibitem{lee}{\sc E.T.Y.~Lee}:
{\it Choosing nodes in parametric curve interpolation, Computer-Aided Design}. pages 363-370, (http://www.sciencedirect.com/science/article\-/pii/0010448589900031), 1989.
\bibitem {doessegger} {\sc S.~D{\"o}ssegger}:
{\it Time-optimal trajectories for a Ballbot}. BSc thesis, ETH Zurich, 2010.
\bibitem{mellinger}{\sc D.~Mellinger, V.~Kumar}:
{\it Minimum Snap Trajectory Generation and Control for Quadrotors}.IEEE International Conference on robotics and Automation, Shanghai, 2011.
\bibitem {biagiotti} {\sc L.~Biagiotti, C.~Melchiorri}:
{\it Trajectory Planning for Automatic Machines and Robots}. Springer Verlag, 2008.
\bibitem {engeln} {\sc G.~Engeln-M{\"u}llges, K.~Niederdrenk, R.~Wodicka}:
{\it Numerik-Algorithmen : Verfahren, Beispiele, Anwendungen}. Springer Verlag, 2011.
\bibitem {williams} {\sc D. L.~Williams}:
{\it Loitering Behaviors of Autonomous Underwater Vehicles}. MSc thesis, Naval Postgraduate School, Monterey, California, 2002.
\bibitem {deluca} {\sc A.~De Luca, G.~Oriolo, C.~Samson}:
{\it Feedback Control of a Nonholonomic Car-Like Robot}. In Robot Motion Planning and Control, pages 171-249, 1998.


%\bibitem{won}{\sc Won Y.~Yang,  [et al.]}:
%{\it Applied Numerical Methods Using MATLAB} . Wiley-Interscience, Hoboken, 2005.

\end{thebibliography}
